---
title: "Data Exploration With R"
author: "Tim Raiswell"
date: "10/15/2018"
output: 
  html_document:
    fig_height: 8
    fig_width: 10
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

### Loading our Libraries  

```{r, warning = FALSE}
pacman::p_load(tidyverse, psych, mosaic, ggeffects)
```

### Importing the Data

```{r, message = FALSE, warning = FALSE}
facebook_data_raw <- read_csv2('https://bit.ly/2NB7vKp')
```

### Looking at the Shape of the Data

```{r, warning = FALSE}
glimpse(facebook_data_raw)
```


### Renaming the data

```{r, warning = FALSE}
facebook_new <- facebook_data_raw %>% 
  rename(page_likes = `Page total likes`, # call the rename function
         type = "Type",
         cat = "Category",
         month = `Post Month`,
         day = `Post Weekday`,
        hour = `Post Hour`,
        paid = "Paid",
        total_reach = `Lifetime Post Total Reach`,
        impressions = `Lifetime Post Total Impressions`,
        engaged_users = `Lifetime Engaged Users`,
        consumers = `Lifetime Post Consumers`,
        consumption = `Lifetime Post Consumptions`,
        impression_by_like =  `Lifetime Post Impressions by people who have liked your Page`,
        reach_liked = `Lifetime Post reach by people who like your Page`,
        like_engage = `Lifetime People who have liked your Page and engaged with your post`,
        interactions = `Total Interactions`)
```

### How did we do?

```{r, warning = FALSE}
glimpse(facebook_new)
```


### Let's convert the factor variables
```{r, warning = FALSE}
facebook_types <- facebook_new %>% 
  mutate(type = as.factor(type),
         cat = as.factor(cat), 
         paid = as.factor(paid),
         month = as.factor(month),
         day = as.factor(day),
         hour = as.factor(hour))

```


### Renaming ad types to something that is more intuitive
```{r, warning = FALSE}
facebook_comp <- facebook_types %>% 
  mutate(cat = str_replace_all(cat, "1", "action"),
         cat  = str_replace_all(cat, "2", "product"),
         cat  = str_replace_all(cat, "3", "inspiration")) %>% 
  mutate(cat = as.factor(cat)) %>% 
  na.omit


```


### Check our work again
```{r, warning = FALSE}
glimpse(facebook_comp)
```

### Let's take a look at the shape of the numeric variables
```{r, warning = FALSE}

facebook_comp %>%
  select(-type, -cat, -month, -day, -hour,  -paid) %>%
  multi.hist(bcol = "seagreen")

# go here for some great-looking colors. Find the ones you love and start to b uild your own visualization brand: http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf
```

### Let's take a look at inter-variable correlation  

```{r, warning = FALSE}
pairs.panels(facebook_comp)
```



### How many of each type of ad category are there?  

```{r, warning = FALSE}

ggplot(data = facebook_comp) +
  geom_bar(mapping = aes(x = cat), fill = "dodgerblue")
 
```

### How many of each type of ad is there?  


```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_bar(mapping = aes(x = type), fill = "seagreen")
```

### How do ad types relate to ad categories?  

```{r, warning = FALSE}
ggplot(data = facebook_comp, aes(x = cat, fill = type)) +
  geom_bar()

```

### Which ad categories get the most total interactions?  

```{r, warning = FALSE}

ggplot(data = facebook_comp) +
  geom_boxplot(
    mapping = aes(x = reorder(cat, interactions, FUN = mean), y = interactions),
    outlier.color = "dodgerblue",
    fill = "slategray3",
    color = "gray38"
  ) +
  scale_y_continuous(limits = c(0, 500))
```

### Which ad types get the most interactions?  

```{r, warning = FALSE}

ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = reorder(type, interactions, FUN = mean), y = interactions), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```

### Does paying for an ad make a difference to interactions?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = reorder(paid, interactions, FUN = mean), y = interactions), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```

### What if we make 'consumers' our target?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = reorder(cat, consumers, FUN = mean), y = consumers), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 3000))

```

### Ad type versus consumers  

```{r, warning = FALSE}

ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = reorder(type, consumers, FUN = mean), y = consumers), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 3000))
```

### Does paying for an ad make a difference to consumer numbers?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = reorder(paid, consumers, FUN = mean), y = engaged_users), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```

### Which days get the most consumers?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = day, y = consumers), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```


### Which months get the most consumers?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = month, y = consumers), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```

### Which hours get the most consumers?  

```{r, warning = FALSE}
ggplot(data = facebook_comp) +
  geom_boxplot(mapping = aes(x = hour, y = consumers), outlier.color = "dodgerblue", fill = "slategray3", color = "gray38") +
  scale_y_continuous(limits = c(0, 500))
```

### Putting it together into a simple regression model  
We will log-transform consumers in the model because it so right-skewed. We would not deploy this model as we have not robustly tested the linear model using cross-validation or test and training datasets. This regression is still very much in the camp of "exploratory data analysis".
```{r, warning = FALSE, message = FALSE}
facebook_lm <- lm(log(consumers) ~ cat + type + paid + month + day + hour, data = facebook_comp)
summary(facebook_lm)
```

### What is the average effect of ad type on consumer numbers?  

```{r, warning = FALSE, message  =FALSE}
# for three variables, automatic facetting
effects_plot <- ggpredict(facebook_lm, terms = "type")
plot(effects_plot)


```

